%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Kartik S} \\ \vspace{1pt}
    Bengaluru, Karnataka 560066 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 8296149001 ~ \href{mailto:kartikshiv03@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{kartikshiv03@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/kartik26/}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}  ~
    \href{https://github.com/kartik2607}{\raisebox{-0.2\height}\faGithub\ \underline{Github}}
    \vspace{-8pt}
\end{center}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\small HAL, Mission and Combat Systems Research and Design Centre}{November 2023 -- December 2023}
      {R\&D Intern}{Bengaluru, Karnataka}
      \resumeItemListStart
        \resumeItem{Researched the feasibility of using Proximal Policy Optimization (PPO) in reinforcement learning for autonomous aircraft control, utilizing the Tensorforce framework to train agents and optimize takeoff strategies, achieving a takeoff distance of 2,400m on a 5,000m runway.}
        \resumeItem{Analyzed reinforcement learning methods for aircraft control, demonstrating the effectiveness of RL in handling complex scenarios and optimizing takeoff performance through reward-based training.}
        \resumeItem{\textbf{Tools \& Technologies :} Python, Tensorforce, NumPy, Pandas, Matplotlib}
      \resumeItemListEnd
    \resumeSubheading
      {\small Quest Global}{August 2023 -- November 2023}
      {Software Intern}{Bengaluru, Karnataka}
      \resumeItemListStart
        \resumeItem{Developed a PoC using Generative AI to generate embedded code from natural language descriptions. Perpared a dataset of over 1,000 entries and achieved 90\% accuracy through PEFT and LoRA fine-tuning.}
        \resumeItem{Built a TCP/IP client-server application for real-time inferencing, integrating a Streamlit UI for user interaction and demonstrating up to 50\% potential reduction in software development cycles.}
        \resumeItem{Showcased Generative AI's capability to streamline software development, by enhancing code generation accuracy and efficiency.}
        \resumeItem{\textbf{Tools \& Technologies :} Python, Torch, Transformers (Hugging Face), PEFT, LoRA, TRL, Streamlit, TCP/IP}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{\href{https://github.com/kartik2607/Secure-Password-Manager}{Secure Password Manager}} $|$ \emph{Python, MySql}}{April 2024}
          \resumeItemListStart
            \resumeItem{Developed a local password manager with AES-256 encryption, implementing secure storage and retrieval using a master password and device secret.}
            \resumeItem{Designed a user-friendly CLI for adding, retrieving, and generating passwords, including automatic clipboard copying and advanced search functionalities.}
          \resumeItemListEnd
        \vspace{-20pt}
         \resumeProjectHeading
          {\textbf{\href{https://github.com/kartik2607/Voice-Activated-Personal-Assistant}{Voice Activated Personal Assistant}} $|$ \emph{Python, Speech Recognition}}{November 2023}
          \resumeItemListStart
            \resumeItem{Built a voice activated personal assistant using pyttsx3, and SpeechRecognition to handle 7+ tasks like opening apps, fetching movie details, reading the news, google search, sending emails and many more.}
            \resumeItem{Integrated WolframAlpha, weather, and various other APIs for real-time mathematical calculations, weather details and other tasks enhancing functionality and user experience.}
          \resumeItemListEnd
        \vspace{-20pt}
      \resumeProjectHeading
        {{\textbf{\href{https://github.com/kartik2607/Sudoku-Solver}{Sudoku Solver}}} $|$ \emph{C++}}{January 2023}
          \resumeItemListStart
            \resumeItem{Implemented a Sudoku solver using a backtracking algorithm, efficiently solving 9x9 puzzles by adhering to Sudoku constraints with 100\% accuracy.}
          \resumeItemListEnd
        \vspace{-20pt}
        \resumeProjectHeading
          {\textbf{\href{https://github.com/kartik2607/EzPay}{EzPay}} $|$ \emph{Python, MySql, NumPy, Tkinter, Matplotlib}}{February 2022}
          \resumeItemListStart
            \resumeItem{Created a payments application with robust analytics, supporting many users and categorizing various transactions to provide detailed financial insights and saving comparisons.}
            \resumeItem{Implemented robust data management using a protected database to ensure the integrity and confidentiality of user accounts and transaction history.}
            \resumeItem{Created a user-friendly interface and transaction tracking, enhancing financial management and improving savings by up to 30\% through detailed expenditure graphs and analytics.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology, Vellore, Tamil Nadu}{September 2021 -- June 2025}
      {Btech in Computer Science and Engineering with Specialization in Information Secuirty}{\textbf{\small CGPA: 8.88}}
    \resumeSubheading
      {Deens Academy, Bengaluru, Karnataka}{April 2019 -- May 2021}
      {Class XII (CBSE)}{\textbf{\small Percentage: 93\%}}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures And Algorithm
                \item\small DBMS
                \item\small OOPS
                \item Operating Systems
                \item Computer Networks
                \item Information Security
                \item Data Privacy
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, Java, MySQL} \\
     \textbf{Tools}{: VS Code, Jupyter Notebook, Anaconda, Burpsuite} \\
     \textbf{Technologies/Frameworks}{: Numpy, Panda, Huggingface, PEFT, LoRA, Linux, GitHub} \\
    }}
 \end{itemize}
 \vspace{-16pt}
 
\end{document}
